---
title: "README"
author: "Bob Rudis"
date: September 03, 2014
output:
  md_document:
    variant: markdown_github
---

slackr is a package to send webhook API messages to Slack.com channels/users

This package contains functions that make it possible to
interact with slack messaging platform. When you need to share
information/data from Rm rather than resort to copy/paste in e-mails
or other services like Skype, you can use this package to send
well-formatted output from multiple R objects and expressions
to all teammates at the same time with little effort.

The following functions are implemented:

- `slackrSetup` : initialize necessary environment variables
- `slackr` : send stuff to slackr
- `ggslackr` : send `ggplot`s to slack.com
- `slackr_users` : get a data frame of slack.com users (full API token - i.e. not wehbook - required)
- `slackr_channels` : get a data frame of slack.com channels (full API token - i.e. not wehbook - required)

### News

- Version `1.0` released

### Installation

```{r eval=FALSE}
devtools::install_github("hrbrmstr/slackr")
```

```{r echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}
options(width=120)
```

### Usage

```{r eval=FALSE}
library(slackr)

# current verison
packageVersion("slackr")


slackrSetup(channel="#code", 
            url_prefix="http://myslack.slack.com/services/hooks/incoming-webhook?")

slackr(str(iris))

```

### Test Results

```{r}
library(slackr)
library(testthat)

date()

test_dir("tests/")
```

