---
output: rmarkdown::github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r base, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# slackr - send messages to Slack <img src='man/figures/logo.svg' align="right" height="139" />

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/slackr)](https://CRAN.R-project.org/package=slackr)
[![R-CMD-check](https://github.com/mrkaye97/slackr/workflows/R-CMD-check/badge.svg)](https://github.com/mrkaye97/slackr/actions)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
![downloads](http://cranlogs.r-pkg.org/badges/grand-total/slackr)
<!-- badges: end -->


The `slackr` package contains functions to interact with the Slack messaging
platform. When you need to share information/data from R, rather than resorting 
to copy/paste, emails, other services like Skype, you can use this package to
send well-formatted output from R to all teammates at the same time 
with little effort. You can send text, R function output, images 
from the current graphics device and `ggplots`, R objects (as R data files), 
rendered LaTeX expressions, and uploaded files.

## Installation

```{r setup, eval=FALSE}
# CRAN version
install.packages("slackr")

# Development version
devtools::install_github("mrkaye97/slackr")
```


## Breaking Changes

Version 2.0.0+ is updated to work with the new Slack API structure!


## Setup

There are two ways of interfacing with `slackr` that provide
significantly different functionality:

1. Creating a single-channel bot

    Using only a webhook to send messages to a channel


2.  Creating a fully-functional multi-channel bot

    Creating a bot user to send messages to multiple channels, including plots,
tables, files, etc. as well as deleting messages, reading the channels in a
workspace, etc.

In most cases, we recommend `Option 1` above. This requires the fewest
permissions and is the simplest to set up, and will allow basic messaging to a
specific channel.

See the vignettes for setup instructions.

### Config File Setup

The `slackr_setup()` function will try to read setup values from a `~/.slackr`
(you can change the default) configuration file, which may be easier and more
secure than passing them in manually (plus, will allow you to have multiple
`slackr` configurations for multiple Slack.com teams).

The file is in Debian Control File (DCF) format since it really doesn't need to
be JSON and R has a handy `read.dcf()` function since that's what `DESCRIPTION`
files are coded in.

Here's the basic format for the configuration file:

```
bot_user_oauth_token: Your app's bot user OAuth token
channel: #general
username: slackr
incoming_webhook_url: https://hooks.slack.com/services/XXXXX/XXXXX/XXXXX
```

You can also change the default emoji icon (from the one you setup at
integration creation time) with `icon_emoji`.

## Contributors

Many thanks to:

- [Bob Rudis](https://github.com/hrbrmstr)
- [Jay Jacobs](https://github.com/jayjacobs)
- [David Severski](https://github.com/davidski)
- [Quinn Weber](https://github.com/qsweber)
- [Konrad Karczewski](https://github.com/konradjk)
- [Ed Niles](https://github.com/eniles)
- [Rick Saporta](https://github.com/rsaporta)
- [Jonathan Sidi](https://github.com/yonicd)
- [Matt Kaye](https://github.com/mrkaye97)
- [Xinye Li](https://github.com/xinye1)
- [Andrie de Vries](https://github.com/andrie)

for their contributions to the package!

## Known Issues

* Depending on your scopes, `slackr` could quietly fail (i.e. not throw an error, but also not post anything to your channel). If this happens, try explicitly adding the app you're trying to have `slackr` post as to the channel you want in your Slack workspace with `/invite @your_app_name` or make sure you have `chat:write.public` enabled.


