---
title: "Multi-Functional Bot Setup"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Multi-Functional Bot Setup}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(slackr)
```


### Multi-Functional Bot Setup

Setting up the multi-functional bot is slightly more complex than the single-channel one. 

1. Go to [https://api.slack.com/apps](https://api.slack.com/apps)
2. Click "Create New App" and then follow the setup instructions
3. Click "OAuth & Permissions" under "Features"
4. Enable the following scopes in order to get all of the functionality:
  * `channels:read`
  * `users:read`
  * `files:read`
  * `groups:read`
  * `groups:write`
  * `chat:write`
  * `chat:write.customize`
  * `chat:write.public`
  * `im:write`
  * `incoming-webhook`
  * `channels:history`
5. Click "Install to Workspace"
6. Select a channel (for webhook messages)
7. Copy the Bot User OAuth Access Token
8. Click "Incoming Webhooks" under "Features"
9. Copy the Webhook URL
8. Call 
```
slackr_setup(channel = '#channel_with_webhook', 
             bot_user_oauth_token = 'your_token', 
             incoming_webhook_url = 'your_webhook')
``` 

You can also follow the config file setup directions below instead of passing the channel, token, and webhook directly.

And that's it! You should be able to post a message with `slackr('test message')`


### Scopes

Without all of the scopes enabled, only certain functions will work. Which ones depends on which scopes you have enabled. See the function documentation for which scopes are needed for that function.

### Known Issues

* Depending on your scopes, `slackr` could quietly fail (i.e. not throw an error, but also not post anything to your channel). If this happens, try explicitly adding the `slackr` app to your channel in your Slack workspace with `/invite @your_app_name` or make sure you have `chat:write.public` enabled.
* Sometimes, channels may not show up in your workspace. If this happens, try running `R.cache::clearCache()`.

### LaTeX for `tex_slackr`

The new function `tex_slackr` in versions `2.0.0+` requires package [`texPreview`](https://github.com/yonicd/texPreview) which is lazy-loaded when the former is called.

For setting up LaTeX see [`texPreview`'s System Requirements](https://github.com/yonicd/texPreview#functionality), and for specific OS setup check out its Github Actions like [this MacOS example](https://github.com/yonicd/texPreview/blob/master/.github/workflows/R-mac.yml#L46).

### Usage 

```{r demo2, eval=FALSE}
slackr_setup(channel="#channel", 
             incoming_webhook_url="https://hooks.slack.com/services/XXXXX/XXXXX/XXXXX",
             bot_user_oauth_token='token')

slackr(str(iris))

# send images
library(ggplot2)
qplot(mpg, wt, data=mtcars)
slackr_dev("#results")

barplot(VADeaths)
slackr_dev("@jayjacobs")

ggslackr(qplot(mpg, wt, data=mtcars))

```

# Onexit Usage

```{r,eval=FALSE}
 ctl <- c(4.17,5.58,5.18,6.11,4.50,4.61,5.17,4.53,5.33,5.14)
 trt <- c(4.81,4.17,4.41,3.59,5.87,3.83,6.03,4.89,4.32,4.69)
 group <- gl(2, 10, 20, labels = c("Ctl","Trt"))
 weight <- c(ctl, trt)

 #pass a message to Slack channel 'general'
 register_onexit(lm,'bazinga!',channel="#general")

 lm.D9 <- slack_lm(weight ~ group)

 #test that output keeps inheritance
 summary(lm.D9)

 #pass a message to Slack channel 'general' with a header message to begin output
 register_onexit(lm,'bazinga!',
 channel="#general",
 header_msg='This is a message to begin')

 lm.D9 <- slack_lm(weight ~ group)

 #onexit with an expression that calls lm.plot
 register_onexit(lm,{
  par(mfrow = c(2, 2), oma = c(0, 0, 2, 0))
  plot(z) #z is the internal output of stats::lm()
 },
 channel="#general",
 header_msg = 'This is a plot just for this output',
 use_device = TRUE)

 lm.D9 <- slack_lm(weight ~ group)

#clean up slack channel from examples
delete_slackr(count = 6,channel = '#general')
```

